### 2020-06-06 README.Rmd
map_wind_exposure edit
changed exposed to a certain winds during a storm to exposed to a certain wind speed during a storm.
add_track = FALSE
In the example code to customize the display of the map_track I added add_track = FALSE in the code above to illustrate this example, although the code doesn't appear to do anything different.

You can use the `map_wind_exposure` function to map counties exposed to a certain winds during a storm. For example, to identify all counties exposed to sustained winds of 20 m / s or higher during Hurricane Katrina, you can run:

@@

```{r fig.width = 7, fig.height = 4}
floyd_map <- map_event_exposure(storm = "Floyd-1999", event_type = "flood")
map_tracks(storms = "Floyd-1999", plot_object = floyd_map, plot_points = TRUE, 
           color = "darkgray")
```

>>>>

You can use the `map_wind_exposure` function to map counties exposed to a certain wind speed during a storm. For example, to identify all counties exposed to sustained winds of 20 m / s or higher during Hurricane Katrina, you can run:

@@

```{r fig.width = 7, fig.height = 4}
floyd_map <- map_event_exposure(storm = "Floyd-1999", event_type = "flood", add_track = FALSE)
map_tracks(storms = "Floyd-1999", plot_object = floyd_map, plot_points = TRUE, 
           color = "darkgray")
```
